Towards Automated Refactoring of Code Clones in Object-Oriented Programming Languages\\- Work in Progress -

### 2019-07-01 sattose/paper.tex
Working on image stuff

\section{Experiments}
This section outlines the conducted experiments to determine refactoring opportunities for code clones. First, we look into the thresholds that determine whether duplicated fragments are considered a clone in section \ref{chap:thresholds}. Next, we show the corpus on which we have performed our measurements in section \ref{chap:corpus}. We then perform an analysis on the context of code clones in section \ref{chap:clonecontextexpl}. Finally, we map refactoring opportunities for clones in section \ref{chap:mergingdups}.

\subsection{The corpus}\label{chap:corpus}
For our experiments we use a large corpus of open source projects~\cite{githubCorpus2013}. This corpus has been assembled to contain relatively higher quality projects. Also, any duplicate projects were removed from this corpus. This results in a variety of Java projects that reflect the quality of average open source Java systems and are useful to perform measurements on. We filtered this corpus further to only include projects that use Maven, which is a build tool which is mainly used to manage dependencies in the Java ecosystem. We then filtered the corpus further to only include projects for which all external dependencies are available. This resulted in 1.343 projects of varying sizes averaging at 980 source lines of code (omitting whitespace, comments) per project.

@@

\subsection{Clone types}
In this chapter we display the differences between clone type 1-3~\cite{roy2007survey} and type 1R-3R as proposed in section \ref{sec:rtypes}. When running our clone detection script over the corpus, we get the results displayed in Fig.~\ref{fig:typeres}.

\begin{figure}[H]
  \caption{Number of cloned declarations/statements.}
    \includegraphics[width=.96\columnwidth]{img/TypeResults}
  \label{fig:typeres}
\end{figure}

@@

\begin{figure}[H]
  \caption{Duration in minutes of identifying clones for clone type definitions.}
    \includegraphics[width=.96\columnwidth]{img/DurationChart}
  \label{fig:performance}
\end{figure}

@@

\subsection{Relations Between Clone Instances} \label{chap:relationsinstances}
When merging code clones in object-oriented languages, it is important to consider the inheritance relation between clone instances. This relation has a big impact on how a clone should be refactored.

\subsubsection{Categorizing Clone Instance Relations}\label{chap:catcloneinstancerelations}
Fontana et al.~\cite{fontana2015duplicated} describe measurements on 50 open source projects on the relation of clone instances to each other. To do this, they first define several categories for the relation between clone instances in object-oriented languages. These categories are shown in Fig.~\ref{fig:clonerelation}. These categories are as follows:
\begin{enumerate}
  \item \textbf{Same method}: All instances of the clone class are in the same method.
  \item \textbf{Same class}: All instances of the clone class are in the same class.
  \item \textbf{Superclass}: All instances of the clone class are children and parents of each other.
  \item \textbf{Ancestor class}: All instances of the clone class are superclasses except for the direct superclass.
  \item \textbf{Sibling class}: All instances of the clone class have the same parent class.
  \item \textbf{First cousin class}: All instances of the clone class have the same grandparent class.
\item \textbf{Common hierarchy class}: All instances of the clone class belong to the same hierarchy, but do not belong to any of the other categories.
\item \textbf{Same external superclass}: All instances of the clone class have the same superclass, but this superclass is not included in the project but part of a library.
\item \textbf{Unrelated class}: There is at least one instance in the clone class that is not in the same hierarchy.
\end{enumerate}

>>>>

\section{Experiments}
This section outlines the conducted experiments to determine refactoring opportunities for code clones. We show the corpus on which we have performed our measurements in section \ref{chap:corpus}. Next, we look into the thresholds that determine whether duplicated fragments are considered a clone in section \ref{chap:thresholds}. We then show a comparison between the different proposed clone types in section \ref{sec:clonetypeexperiments}. Afterwards, we perform an analysis on the context of code clones in section \ref{chap:clonecontextexpl}. Finally, we map refactoring opportunities for clones in section \ref{chap:mergingdups}.

All experiments were conducted using CloneRefactor, which contains scripts for running large scale clone detection over the indicated corpus.

\subsection{The corpus}\label{chap:corpus}
For our experiments we use a large corpus of open source projects~\cite{githubCorpus2013}. This corpus has been assembled to contain relatively higher quality projects. Also, any duplicate projects and files were removed from this corpus. This results in a variety of Java projects that reflect the quality of average open source Java systems and are useful to perform measurements on. We filtered this corpus further to only include projects that use Maven, which is a build tool which is mainly used to manage dependencies in the Java ecosystem. We then filtered the corpus further to only include projects for which all external dependencies are available, as CloneRefactor requires all dependencies of a project in order to accurately resolve all its symbols. This resulted in 1.343 projects of varying sizes averaging at 980 source lines of code (omitting whitespace, comments) per project.

@@

\subsection{Clone types}\label{sec:clonetypeexperiments}
In this chapter we display the differences between clone type 1-3~\cite{roy2007survey} and type 1R-3R as proposed in section \ref{sec:rtypes}. When running our clone detection script over the corpus, we get the results displayed in Fig.~\ref{fig:typeres}.

\begin{figure}[H]
  \caption{Number of cloned declarations/statements.}
    \includegraphics[width=1\columnwidth]{img/TypeResults}
  \label{fig:typeres}
\end{figure}

@@

\begin{figure}[H]
  \caption{Duration in minutes of identifying clones for clone type definitions.}
    \includegraphics[width=1\columnwidth]{img/DurationChart}
  \label{fig:performance}
\end{figure}

@@

\subsubsection{Relations Between Clone Instances} \label{chap:relationsinstances}
When merging code clones in object-oriented languages, it is important to consider the inheritance relation between clone instances. This relation has a big impact on how a clone should be refactored.

Fontana et al.~\cite{fontana2015duplicated} describe measurements on 50 open source projects on the relation of clone instances to each other. To do this, they first define several categories for the relation between clone instances in object-oriented languages. These categories are shown in Fig.~\ref{fig:clonerelation}. These categories are as follows:
\begin{enumerate}
  \item \textbf{Same method}: All instances of the clone class are in the same method.
  \item \textbf{Same class}: All instances of the clone class are in the same class.
  \item \textbf{Superclass}: All instances of the clone class are children and parents of each other.
  \item \textbf{Ancestor class}: All instances of the clone class are superclasses except for the direct superclass.
  \item \textbf{Sibling class}: All instances of the clone class have the same parent class.
  \item \textbf{First cousin class}: All instances of the clone class have the same grandparent class.
\item \textbf{Common hierarchy class}: All instances of the clone class belong to the same hierarchy, but do not belong to any of the other categories.
\item \textbf{Same external superclass}: All instances of the clone class have the same superclass, but this superclass is not included in the project but part of a library.
\item \textbf{Unrelated class}: There is at least one instance in the clone class that is not in the same hierarchy.
\end{enumerate}
